Existence of Forward Simulations for Particular Data Structures

### 2017-01-22 draft.tex
Refined TSS fs relation definition

The relation $fs \subseteq Q_C \rightarrow Q_{AbsS}$ contains $(s,t)$ iff the following are satisfied:
\begin{itemize}
\item[\emph{Nodes}] $k \in O_t$ iff $k$ is a push operation in $s$ ($k \in O_a$) such that either it has not inserted its node to the pool yet ( $cp_s(k) = A_i$ and $i<3$) or its node is not taken by a pop ($cp_s(k) = A_i$, $i\geq 3$ and $n_s(k)->taken = false$). 
\item[\emph{Pend/Comp}] A vertex $k \in O_t$ is pending ($\ell_t(k) = (d, \texttt{PEND})$) iff $k$ satisfies the previous condition, $x_s(k) = d$ and it is not completed in $s$ ($cp_s(k) = A_i$ and $i<6$). Similarly, this vertex is completed ($\ell_t(k) = (d, \texttt{COMP})$) iff $k$ satisfies the previous condition, $x_s(k) = d$ and it is completed in $s$ ($cp_s(k) = A_6$). 
\item[\emph{TSOrder}] If a node has a smaller timestamp than the other node in $s$, the operations that inserted them cannot be ordered reversely in $t$. More formally, let $k, k' \in O_t$ s.t. $n_s(k)-> ts < n_s(k')->ts$. Then, $k \nless_t k'$.
\item[\emph{TidOrder}] Order among the nodes inserted by the same threads in $s$ must be preserved among the operations that inserted them in $t$. Let $k, k' \in O_t$ s.t. $myTid_s(k) = myTid_s(k')$ and $n_s(k)->ts < n_s(k')->ts$. Then, $k <_t k'$.
\item[Frontiers] Every maximally closed or pending vertex can be removed by a pending pop. More formally, let $k \in O_t$ such that $\ell_t(k) = (\_,\texttt{PEND})$. Then, for all pops $p$, $k \in ov_t(p)$. In the other case, let $k \in O_t$ such that $\ell_t(k) = (\_,\texttt{COMP})$ and for all other $k' \in O_t$ such that $k<_t k'$, we know $\ell_t(k') = (\_,\texttt{PEND})$. Then, for all pop operations $p$, $k \in be_t(p)$ or $k \in ov_t(p)$. 
\item[\emph{MaximalOV}] If a push $k \in O_t$ is a candidate to be removed by a pop $p$, then every other push $k'$ invoked after $k$ is a candidate to be removed by $p$ since $k$ is concurrent with $p$. More formally, let $k, k' \in O_t$ such that $k <_t k'$ and there exists a pop $p$ such that $k \in be_t(p)$ or $k \in ov_t(p)$. Then, $k' \in ov_t(p)$.
\item[\emph{MinimalBE}] If a push $k \in O_t$ has finished before the pop $p$ is invoked and yet $k$ is a candidate to be removed by $p$, other pushes completed before $k$ can not be candidates to be removed by $p$ at that state. More formally, let $k, k' \in O_t$ such that $k <_t k'$ and there exists a pop $p$ such that $k' \in be_t(p)$. Then, neither $k \in be_t(p)$ nor $k \in ov_t(b)$.
\item[\emph{ReverseFrontiers}] If a push $k \in O_t$ is concurrent with the pop $p$ and there exists another push $k' \in O_t$ that is immediate predecessor of $k$, then $k'$ is either concurrent or maximally closed with respect to $p$. More formally, let $k, k' \in O_t$ such that $k' \in pred_{<_t}(k)$ and $k \in ov_t(p)$ for some pop $p$. Then, either $k' \in ov_t(p)$ or $k' \in be_t(p)$. 
\item[\emph{TraverseBefore}] If a pop operation $p$ is currently visiting node $n$ and there is a node $m$ coming before $n$ in the traverse order with a greater timestamp, then the operation that inserts $m$ must be concurrent with $p$. More formally, let $k \in O_t$ such that $n_s(k) <^{tr}_s n_s(p)$ and $n_s(k)->ts > n_s(p)->ts$. Then, $k \in ov_t(p)$.
\item[\emph{TraverseAfter}] If a pop operation $p$ is currently visiting node $n$ and its youngest element $m$ is still not taken in state $s$, then either $m$ is a candidate to be removed by $p$ in $t$ or there exists a later node $m'$ than $n$ such that $m'$ is a candidate in $t$ it has a bigger timestamp than n. More formally, let $k, k' \in O_t$ such that $youngest_s(p) = n_s(k)$ and $n_s(k') = n_s(p)$. Then, either $k \in ov_t(p) \vee k \in be_t(p)$ or there exists $k'' \in O_t$ s.t. $n_s(k'')->ts > n_s(k) ->ts$ and $k'' \in ov_t(p) \vee k'' \in be_t(p)$ and either $k' <^{tr}_s k''$ or $n_s(p) = n_s(k'') \wedge cp_s(p) = R_j \wedge j>3$. 
\end{itemize}
\end{proof}

>>>>

The relation $fs \subseteq Q_C \rightarrow Q_{AbsS}$ contains $(s,t)$ iff the following are satisfied:
\begin{itemize}
\item[\emph{Nodes}] $k \in O_t$ iff $k$ is a push operation in $s$ ($k \in O_a$) such that either it has not inserted its node to the pool yet ( $cp_s(k) = A_i$ and $i<3$) or its node is not taken by a pop ($cp_s(k) = A_i$, $i\geq 3$ and $n_s(k)->taken = false$). 
\item[\emph{Pend/Comp}] A vertex $k \in O_t$ is pending ($\ell_t(k) = (d, \texttt{PEND})$) iff $k$ satisfies the previous condition, $x_s(k) = d$ and it is not completed in $s$ ($cp_s(k) = A_i$ and $i<6$). Similarly, this vertex is completed ($\ell_t(k) = (d, \texttt{COMP})$) iff $k$ satisfies the previous condition, $x_s(k) = d$ and it is completed in $s$ ($cp_s(k) = A_6$). Pending vertices are maximal with respect to $<_t$ i.e., if $k \in O_t$ is a pending vertex, then for all $k' \in O_t$ $k \nless_t k'$.
\item[\emph{TSOrder}] If a node has a smaller timestamp than the other node in $s$, the operations that inserted them cannot be ordered reversely in $t$. More formally, let $k, k' \in O_t$ s.t. $n_s(k)-> ts \leq n_s(k')->ts$. Then, $k' \nless_t k$.
\item[\emph{TidOrder}] Order among the nodes inserted by the same threads in $s$ must be preserved among the operations that inserted them in $t$. Let $k, k' \in O_t$ s.t. $myTid_s(k) = myTid_s(k')$ and $n_s(k)->ts < n_s(k')->ts$. Then, $k <_t k'$.
\item[Frontiers] Every maximally closed or pending vertex can be removed by a pending pop. More formally, let $k \in O_t$ such that $\ell_t(k) = (\_,\texttt{PEND})$. Then, for all pops $p$, $k \in ov_t(p)$. In the other case, let $k \in O_t$ such that $\ell_t(k) = (\_,\texttt{COMP})$ and for all other $k' \in O_t$ such that $k<_t k'$, we know $\ell_t(k') = (\_,\texttt{PEND})$. Then, for all pop operations $p$, $k \in be_t(p)$ or $k \in ov_t(p)$. 
\item[\emph{MaximalOV}] If a push $k \in O_t$ is a candidate to be removed by a pop $p$, then every other push $k'$ invoked after $k$ is a candidate to be removed by $p$ since $k$ is concurrent with $p$. More formally, let $k, k' \in O_t$ such that $k <_t k'$ and there exists a pop $p$ such that $k \in be_t(p)$ or $k \in ov_t(p)$. Then, $k' \in ov_t(p)$.
\item[\emph{MinimalBE}] If a push $k \in O_t$ has finished before the pop $p$ is invoked and yet $k$ is a candidate to be removed by $p$, other pushes completed before $k$ can not be candidates to be removed by $p$ at that state. More formally, let $k, k' \in O_t$ such that $k <_t k'$ and there exists a pop $p$ such that $k' \in be_t(p)$. Then, neither $k \in be_t(p)$ nor $k \in ov_t(b)$.
\item[\emph{ReverseFrontiers}] If a push $k \in O_t$ is concurrent with the pop $p$ and there exists another push $k' \in O_t$ that is immediate predecessor of $k$, then $k'$ is either concurrent or maximally closed with respect to $p$. More formally, let $k, k' \in O_t$ such that $k' \in pred_{<_t}(k)$ and $k \in ov_t(p)$ for some pop $p$. Then, either $k' \in ov_t(p)$ or $k' \in be_t(p)$. 
\item[\emph{TraverseBefore}] If a pop operation $p$ is currently visiting node $n$ and there is a node $m$ coming before $n$ in the traverse order with a greater timestamp, then the operation that inserts $m$ must be concurrent with $p$. More formally, let $k \in O_t$ such that $n_s(k) <^{tr}_s n_s(p)$ and $n_s(k)->ts > n_s(p)->ts$. Then, $k \in ov_t(p)$.
\item[\emph{TraverseAfter}] If a pop operation $p$ is currently visiting node $n$ that is not null and its youngest element $m$ is not null and still not taken in state $s$, then either $m$ is a candidate to be removed by $p$ in $t$ or there exists a later node $m'$ than $n$ such that $m'$ is a candidate in $t$ it has a bigger timestamp than n. More formally, assume that there exists $k, k' \in O_t$ such that $youngest_s(p) = n_s(k)$ and $n_s(k') = n_s(p)$. Then, either $k \in ov_t(p) \vee k \in be_t(p)$ or there exists $k'' \in O_t$ s.t. $n_s(k'')->ts > n_s(k) ->ts$ and $k'' \in ov_t(p) \vee k'' \in be_t(p)$ and either $k' <^{tr}_s k''$ or $n_s(p) = n_s(k'') \wedge cp_s(p) = R_j \wedge j>3$. 
\end{itemize}
\end{proof}
